### 2023-06-30 journal/related.tex
Updated information about Haas queue

>>>>

Haas \cite{Haa15} described a queue implementation based on timestamping.
% This queue is also sketched in \cite{DHK15}.
% A different? linearizability proof for this queue appears in Khyza et al.\ \cite{KDGP17}.
To enqueue an item, a process adds the item, together with an associated timestamp,
to the process's own single-enqueuer multi-dequeuer queue, which is implemented as a linked list.  
Items added by concurrent enqueues may get the same timestamp.
Although enqueues are very efficient, dequeues look at all $p$ lists
to find and return an item with the oldest timestamp.
This is compounded by the fact that dequeues may compete to claim the same item using a CAS, resulting
in a CAS retry problem.  As a result, the amortized step complexity for dequeue operations
is $\Omega(p^2)$.
